### 2021-07-09 doc/thesis/chapters/deployment-on-hardware.tex
Thesis chapter "signal processing theory" text. (#20)

%%%%%%%%%%%%%%%%%%%%
\chapter{Signal Processing Theory}
\label{cha:TheThesis}

  \section{Modulation from Baseband to RF}
  \section{Modulation from RF to Baseband}

  \section{Frequency Modulation (FM)}
  see literature/Present\_lec6\_AM\_FM.pdf\\
  see lectures out of HSD/ESD
    \subsection{Mathematical description}
    \subsection{Frequency Band, Channel allocation/distribution}

  \section{Algorithms for Digital FM Demodulation}
    see literature/FmDemodulator.pdf (Sect. 3.3)
    see literature/00476180 Digital FM Demodulator for FM, TV, and Wireless.pdf (Sect. II and III)

    \subsection{Baseband Delay Demodulator}
    \subsection{Phase-Adapter Demodulator}
    \subsection{Phase-Locked Loop (PLL)}
    \subsection{Mixed Demodulator}

%%%%%%%%%%%%%%%%%%%%
\chapter{High-Level Synthesis}
  \section{Introduction / State of the Art}
  \section{Functionality (transform high-level code to HDL)}
  \section{Language Support}
    \subsection{C++}
    \subsection{SystemC}
  \section{Coding}
    \subsection{Compiler Directives (\#pragma's)}
    \subsection{Data types}
    \subsection{Functions}
    \subsection{Loops}
    \subsection{Conditional statements}
  \section{Advantages / Disadvantages}
    easy and much faster to get complex HDL code, such as image/video processing, through libraries like OpenCV. However, it is less optimized, and a developer still needs to have a strong hardware background, to be able to understand what is being generated in hardware from x lines of code in HLS/Cpp.

%%%%%%%%%%%%%%%%%%%%
\chapter{System Architecture/Concept}
  \section{Block Diagram (with details)}
    \subsection{describe blocks}
  \section{Which parts in HLS and VHDL}
  \section{Test Environment}

%%%%%%%%%%%%%%%%%%%%
\chapter{Implementation}
  \section{Matlab/Python Model}
  in fixed point, close to hardware level algorithm

  \section{VHDL (no shortcut)}
    \subsection{Channel Selection (IF to Channel-BB)}
    \subsection{Phase Detector}
    \subsection{other Elements}

  \section{High-Level Synthesis}
    \subsection{Channel Selection (IF to Channel-BB)}
    \subsection{Phase Detector}
    \subsection{other Elements}

  \section{Common Testbench}
    \subsection{Architecture (same tb for VHDL and HLS-generated HDL)}
    \subsection{Framework cocotb, with ghdl compiler}
        Instantiate both HDL models in the testbench.\\
        Display a direct comparison of outputs in graphs. This is practical, since the cocotb framework runs in python and graphs can be generated using Python's matplotlib.

  \section{Develop HLS compiler independent code (optional)}
    \subsection{Challenges}
     Different compilers use different \#pragmas, etc.\\
     The \#pragmas need to be within the code, at the appropriate positions, which makes it difficult to write compiler independent code....

\chapter{Test Results}
  \section{Functionality}
  % Functionality same?
  % Sim speed of x min of recorded FM signal
  % lines of code
  \subsection{Implementation effort/time}
  \subsection{Hardware Utilization}
  \subsection{Others}

  % TODO Überlegungen in diesem Kapitel
  % kann Demodulator geändert werden? Bsp. von FM zu DAB+, QAM, etc..
  % - von matlab heraus VHDL generieren, etc

%%%%%%%%%%%%%%%%%%%%
\chapter{Deployment on Hardware}
  \section{Hardware Platform}
    \subsection{RTL2832u Dongle}
    \subsection{ZedBoard}

>>>>

%%%%%%%%%%%%%%%%%%%%
\chapter{Deployment on Hardware}
\label{cha:DeploymentOnHardware}
  \section{Hardware Platform}
    \subsection{RTL2832u Dongle}
    \subsection{ZedBoard}

### 2021-07-09 doc/thesis/chapters/dsp.tex
Thesis chapter "signal processing theory" text. (#20)

\includepicture [0.9] [0] {
  Frequency spectrum of the sampled baseband signal with its replicas at integer multiples of $f_s$ \cite{ThyagarajanK.S2019ItDS}.\\
  A) $f_s > 2f_{signal}$: $f_s$ is high enough and thus meets the theorem.\\
  B) $f_s = 2f_{signal}$: $f_s$ exactly meets the theorem.\\
  C) $f_s < 2f_{signal}$: $f_s$ is too low and thus creates overlaps of the replicas - aliasing.
} {aliasing_freq_spectrum} {img/draw.io/sampling-aliasing}

@@

\includepicture [0.9] [0] {Allocation of frequencies in an FM channel \cite{FigFmChannelFreqSpectrum}.
} {fm_channel_baseband_freqs} {img/draw.io/fm-channel-baseband-freqs}

@@

\includepicture [0.75] [0] {Time-domain signals in envelope detection \cite{RoppelBegleitmaterial}.} {time_domain_envelope_detect_orig} {img/envelope-detect-time-domain.jpg}

\includepicture [1.0] [0] {Time-domain signals in envelope detection \cite{RoppelBegleitmaterial}.} {time_domain_envelope_detect} {img/draw.io/envelope-detect-time-domain}

>>>>

\includepicture [0.95] [0] {
  Frequency spectrum of the sampled baseband signal with its replicas at integer multiples of $f_s$ \cite{ThyagarajanK.S2019ItDS}.\\
  A) $f_s > 2f_{signal}$: $f_s$ is high enough and thus meets the theorem.\\
  B) $f_s = 2f_{signal}$: $f_s$ exactly meets the theorem.\\
  C) $f_s < 2f_{signal}$: $f_s$ is too low and thus creates overlaps of the replicas - aliasing.
} {aliasing_freq_spectrum} {img/draw.io/sampling-aliasing}

@@

\includepicture [1.0] [0] {Allocation of frequencies in an FM channel \cite{FigFmChannelFreqSpectrum}.} {fm_channel_baseband_freqs} {img/draw.io/fm-channel-baseband-freqs}

@@

\includepicture [1.0] [0] {Time-domain signals in envelope detection \cite{RoppelBegleitmaterial}.} {time_domain_envelope_detect} {img/draw.io/envelope-detect-time-domain.png}

### 2021-07-09 doc/thesis/chapters/introduction.tex
Thesis chapter "signal processing theory" text. (#20)

Therefore, one of the main motivation points of this thesis is to combine several disciplines and multiple implementation methods in a common context of a single project.

In a more general perspective, the current electronics market situation is a huge motivational factor as well.
Smart devices, smart sensors, Internet of Things (IoT) and many similar terms are well-known and are becoming more and more present in the publics daily lives.
In some degree, all of these devices represent embedded systems, since they all consist of processing units, combined with sensors and interfaces to communicate with their outside world.
In the future, the number of devices and the range of applications in this area is likely going to grow.
This will require a lot of engineering work to advance the state of technology we have today and explore new areas of application.
Since the development of an embedded system combines so many displines, it is of advantage to have knowledge of as many as possible of them.
However, not only understanding single parts, but to have an overview and understanding of the entire, integrated system and the interaction between those single parts is important in an embedded system.

Those major reasons lead to the choice of topic for this thesis - understanding all the single parts by themselves, while maintaining the understanding over an interated embedded system that fulfills a task as a whole.

@@

In order to elaborate on the theoretical topics of this thesis, a comprehensive practical project is developed along with it.
The project of choice is a digital FM broadcast radio receiver.
It combines several disciplines that appear in the master's program Embedded Systems Design, such as digital signal processing (DSP), software development and system design and thus is a perfect candidate for this project.

@@

The main goal of this thesis is to elaborate a system design for an embedded system, that combines all the knowledge of different disciplines and topics that are accumulated over the time of studies in a single project.

This includes the development of a system model in a tool like Matlab, the practical usage and implementation of DSP in an FPGA, the development of a digital receiver and the deployment on actual hardware.

Furthermore, the receiver implementation on the FPGA is to be done in two variants.
The first variant is traditional, manually written hardware description language (HDL) in the programming language VHDL.
For the second variant, high-level synthesis (HLS) is employed, to generate the low-level HDL from high-level C++ code.
These two methods are implemented and compared on the basis of usability and some metrics.

In the view of a system design approach, another focus is put on a sustainable testing and development strategy for the entire system.
Above mentioned implementation variants should optimally share as much as possible of verification code, in order to save time and effort in implementation.
Also, as many tasks as possible should be automated by scripts, to save time in manual labor for the software engineers.
All that enables an efficient development cycle of the product.

>>>>

Therefore, one of the main motivation points of this thesis is to combine several disciplines and multiple implementation methods in a common context of a single project.\\

In a more general perspective, the current electronics market situation is a huge motivational factor as well.
Smart devices, smart sensors, Internet of Things (IoT) and many similar terms are well-known and are becoming more and more present in the publics' daily lives.
In some degree, all of these devices represent embedded systems, since they all consist of processing units, combined with sensors and interfaces to communicate with their outside world.
In the future, the number of devices and the range of applications in this area is going to grow from todays' point of view.
This will require a lot of engineering work to advance the state of technology we have today and explore new areas of application.\\

Since the development of an embedded system combines so many displines, it is of advantage to have knowledge of as many as possible of them.
However, not only understanding single parts, but to have an overview and understanding of the entire, integrated system and the interaction between those single parts is important in an embedded system.\\

Those major reasons lead to the choice of topic for this thesis - understanding all the single parts by themselves, while maintaining the understanding over an integrated embedded system that fulfills a task as a whole.

@@

In order to elaborate on the theoretical topics of this thesis, a comprehensive practical project is developed along with it.
The project of choice is a digital FM broadcast radio receiver.
It combines several disciplines that appear in the master's program Embedded Systems Design, such as digital signal processing (DSP), software development and system design and thus is a perfect candidate for this project.\\

@@

The main goal of this thesis is to elaborate a system design for an embedded system, that combines all the knowledge of different disciplines and topics which are accumulated over the time of the university program, in a single project.

This includes the development of a system model in a tool like Matlab, the practical usage and implementation of DSP in an FPGA, the development of a digital receiver and the deployment on actual hardware.\\

The receiver implementation on the FPGA is to be done in two variants.
The first variant is traditional, manually written hardware description language (HDL) in the programming language VHDL, as it has been done for years.
For the second variant, high-level synthesis (HLS) is employed, to generate the low-level HDL from high-level \cplusplus code.
These two methods are implemented and compared on the basis of usability and some metrics.

In the view of a system design approach, another focus is put on a sustainable testing and development strategy for the entire system.
Above mentioned implementation variants should optimally share as much as possible of testing and verification code, in order to save time and effort in implementation.
Also, as many tasks as possible should be automated by scripts, to save time in manual labor for the engineers working on the development.
All that enables an efficient development cycle of the product.\\

### 2021-07-09 doc/thesis/chapters/results.tex
Thesis chapter "signal processing theory" text. (#20)

%%%%%%%%%%%%%%%%%%%%
\chapter{Signal Processing Theory}
\label{cha:TheThesis}

  \section{Modulation from Baseband to RF}
  \section{Modulation from RF to Baseband}

  \section{Frequency Modulation (FM)}
  see literature/Present\_lec6\_AM\_FM.pdf\\
  see lectures out of HSD/ESD
    \subsection{Mathematical description}
    \subsection{Frequency Band, Channel allocation/distribution}

  \section{Algorithms for Digital FM Demodulation}
    see literature/FmDemodulator.pdf (Sect. 3.3)
    see literature/00476180 Digital FM Demodulator for FM, TV, and Wireless.pdf (Sect. II and III)

    \subsection{Baseband Delay Demodulator}
    \subsection{Phase-Adapter Demodulator}
    \subsection{Phase-Locked Loop (PLL)}
    \subsection{Mixed Demodulator}

%%%%%%%%%%%%%%%%%%%%
\chapter{High-Level Synthesis}
  \section{Introduction / State of the Art}
  \section{Functionality (transform high-level code to HDL)}
  \section{Language Support}
    \subsection{C++}
    \subsection{SystemC}
  \section{Coding}
    \subsection{Compiler Directives (\#pragma's)}
    \subsection{Data types}
    \subsection{Functions}
    \subsection{Loops}
    \subsection{Conditional statements}
  \section{Advantages / Disadvantages}
    easy and much faster to get complex HDL code, such as image/video processing, through libraries like OpenCV. However, it is less optimized, and a developer still needs to have a strong hardware background, to be able to understand what is being generated in hardware from x lines of code in HLS/Cpp.

%%%%%%%%%%%%%%%%%%%%
\chapter{System Architecture/Concept}
  \section{Block Diagram (with details)}
    \subsection{describe blocks}
  \section{Which parts in HLS and VHDL}
  \section{Test Environment}

%%%%%%%%%%%%%%%%%%%%
\chapter{Implementation}
  \section{Matlab/Python Model}
  in fixed point, close to hardware level algorithm

  \section{VHDL (no shortcut)}
    \subsection{Channel Selection (IF to Channel-BB)}
    \subsection{Phase Detector}
    \subsection{other Elements}

  \section{High-Level Synthesis}
    \subsection{Channel Selection (IF to Channel-BB)}
    \subsection{Phase Detector}
    \subsection{other Elements}

  \section{Common Testbench}
    \subsection{Architecture (same tb for VHDL and HLS-generated HDL)}
    \subsection{Framework cocotb, with ghdl compiler}
        Instantiate both HDL models in the testbench.\\
        Display a direct comparison of outputs in graphs. This is practical, since the cocotb framework runs in python and graphs can be generated using Python's matplotlib.

  \section{Develop HLS compiler independent code (optional)}
    \subsection{Challenges}
     Different compilers use different \#pragmas, etc.\\
     The \#pragmas need to be within the code, at the appropriate positions, which makes it difficult to write compiler independent code....

\chapter{Test Results}
  \section{Functionality}
  % Functionality same?
  % Sim speed of x min of recorded FM signal
  % lines of code
  \subsection{Implementation effort/time}
  \subsection{Hardware Utilization}
  \subsection{Others}

@@

%%%%%%%%%%%%%%%%%%%%
\chapter{Deployment on Hardware}
  \section{Hardware Platform}
    \subsection{RTL2832u Dongle}
    \subsection{ZedBoard}

>>>>

%%%%%%%%%%%%%%%%%%%%
\chapter{Test Results}
\label{cha:Results}
  \section{Functionality}
  % Functionality same?
  % Sim speed of x min of recorded FM signal
  % lines of code
  \subsection{Implementation effort/time}
  \subsection{Hardware Utilization}
  \subsection{Others}

@@
